---
title: "Schedule"
listing:
  - id: schedule
    contents:
      - weeks/Week*.qmd
    type: table
    fields: [title, description, subtitle]
    field-display-names:
      title: "Week"
      description: "Dates"
      subtitle: "Topic"
    date-format: "MMMM DD, YYYY"
    sort: [filename]
    sort-ui: true
    filter-ui: true
 #tbl-colwidths: [5,20,50]
editor: visual
---

```{r packages-data, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)

withr::with_dir(here::here(), {
  schedule_nested <- targets::tar_read(schedule_page_data)
  targets::tar_load(schedule_ical_file)
})

base_url <- yaml::read_yaml(here::here("_quarto.yml"))$website$`site-url`
ical_url_absolute <- paste0(base_url, "/", schedule_ical_file)
```

Here's your roadmap for the year!

Every class session has four important sections. You should read about
the details for each using the main menu at the top of this webpage.

-   [**Week Overview**](/weeks/index.html)
    (<i class="fas fa-binoculars"></i>): This page overviews the weeks

-   [**Lectures**](/lectures/index.html)
    (<i class="fas fa-chalkboard-teacher"></i>): This page is for
    lectures

-   [**Labs**](/labs/index.html) (<i class="fas fa-laptop-code"></i>):
    This page is about labs

-   [**Extras**](/Extras/index.html) (<i class="fas fa-gift"></i>): This
    page is about Extras

-   [**Coursework**](/coursework/index.html)
    (<i class="fas fa-pencil-ruler"></i>): This page contains the
    instructions for either the session exercise (1--3 brief tasks), or
    for the two mini projects and final project. **Assignments are due
    by 11:59 PM on the day they're listed.**

-   [**Mini-Diss**](/Mini-Diss/index.html)
    (<i class="fas fa-book-bookmark"></i>): This page contains an
    interactive lesson that teaches you the principles and code you need
    to know. Go through these after doing the content.

::: {.row .d-flex .justify-content-center}
::: {.col-12 .col-sm-10 .col-md-6}
::: {.card .bg-danger .text-white}
::: card-body
**tl;dr**: You should follow this general process each week:

-   Check out the overview (<i class="fas fa-binoculars"></i>) page and
    do any thinking/reading/prep suggested if you have the chance
-   Come to the lecture (<i class="fas fa-chalkboard-teacher"></i>) page
-   Attend the lab (<i class="fas fa-laptop-code"></i>) and get cracking
-   Complete the coursework (<i class="fas fa-pencil-ruler"></i>) on
    time
-   Use the plentiful Mini-Diss resources
    (<i class="fas fa-book-bookmark"></i>) to help you smash the MD
-   Use the extras (<i class="fas fa-gift"></i>) to keep you in tip top
    spirit
:::
:::
:::
:::

------------------------------------------------------------------------

## Weekly schedule

::: {#schedule}
:::

## Coursework

Here are some assessment items

### Homework

2 hrs per week

### Labs

2 hrs per week

### Exams

2 hrs face to face

::: callout-tip
## Subscribe!

You can subscribe to this calendar URL in Outlook, Google Calendar, or
Apple Calendar:

::: grid
::: {.g-col-12 .g-col-md-2}
<p class="download-btn">

<a class="btn btn-danger btn-sm" href="/`r schedule_ical_file`" role="button">{{< fa calendar-alt >}}
Download</a>

</p>
:::

::: {.g-col-12 .g-col-md-10}
<p><input class="form-control" type="text" value="`r ical_url_absolute`" onclick="this.select()" readonly></p>
:::
:::
:::

```{r build-table, include=FALSE}
show_table <- function(group_id) {
  # Add a heading
  cat(as.character(paste("\n\n###", schedule_nested$group[[group_id]], "\n\n")))
  
  # Make the table
  tbl <- schedule_nested$data[[group_id]] %>% 
    kbl(escape = FALSE, align = "rlcccc", table.attr = 'class="schedule-table"') %>% 
    kable_styling() %>% 
    column_spec(1, width = "20%", extra_css = "padding-right: 20px;") %>% 
    column_spec(2, width = "48%") %>% 
    column_spec(3:6, width = "8%")
  
  cat(tbl)
}
```

```{r show-table, echo=FALSE, results="asis"}
walk(seq(1, nrow(schedule_nested)), ~show_table(.x))
```

:::
